[dcpo_demsupport]

### 2020-07-26 paper/dcpo_demsupport.Rmd
download supdem from dataverse just one time

```{r compare_n}
supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
  read_csv(col_types = "cdcddcdc") %>% 
  janitor::clean_names() %>% 
  with_min_yrs(2)

>>>>

```{r compare_n}
if (!file.exists("data/supdem raw survey marginals.tab")) {
  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
    read_csv(col_types = "cdcddcdc") %>% 
    write_csv("data/supdem raw survey marginals.tab")
}

supdem <- read_csv("data/supdem raw survey marginals.tab",
                   col_types = "cdcddcdc") %>% 
  janitor::clean_names() %>% 
  with_min_yrs(2)
